Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2021-09-08 paper/zhang-cook-laa-langrene-menendez.tex
response to patricia & urtricia & ursula's comments

{\centering \includegraphics[width=0.7\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/tour-path}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/toy-search}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/toy-interp-1}

@@

Several annotations have been made to help understanding this plot. As
mentioned previously, the original basis space is a high-dimensional
sphere and random bases on the sphere can be generated via the
\CRANpkg{geozoo} \citep{geozoo} package. We use PCA to estimate the 2D
space that contains all the bases recorded and the zero basis. The
centre of the 2D view is the first two PC coordinates of the zero
matrix, and the radius is estimated as the largest distance from the
centre to the basis. The theoretical best basis is known for simulated
data and can be labelled to compare how close the end basis found by the
optimisers is to the theoretical best. Various aesthetics, i.e.~size,
alpha (transparency), and colour, are applicable to emphasize critical
elements and adjust for the presentation. For example, anchor points and
search points are less important and hence a smaller size and alpha are
used. Alpha can also be applied on the interpolation paths to show the
start to finish from transparent to opaque.

@@

{\centering \includegraphics[width=1\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/toy-pca}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/toy-pca-animated-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/toy-tour-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/toy-torus-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/interruption-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/polish-1}

@@

The holes index function used for all the examples before this section
produces a smooth interpolation, while this is not the case for all the
indexes. An example of a noisy index function for 1D projections
compares the projected data, \(\mathbf{Y}_{n \times 1}\), to a randomly
generated normal distribution, \(\mathcal{N}_{n \times 1}\), using the
Kolmogorov test. Let \(F_{.}(n)\) be the ECDF function (empirical
cummulative distribution function), with two possible subscripts \(Y\)
and \(\mathcal{N}\) representing the projected and randomly generated
data, and \(n\) denoting the number of observation, the Normal
Kolmogorov index \(I^{nk}(n)\), is defined as:

@@

{\centering \includegraphics[width=1\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/noisy-better-geo}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/kol-result}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/huizezhang/Documents/research/paper-tour-vis/figs/flip-sign}

>>>>

{\centering \includegraphics[width=0.7\linewidth]{/Users/sherryzhang/Documents/researh/paper-tour-vis/figs/tour-path}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/researh/paper-tour-vis/figs/toy-search}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/researh/paper-tour-vis/figs/toy-interp-1}

@@

Several annotations have been made to help understanding this plot. As
mentioned previously, the original basis space is a high-dimensional
sphere and random bases on the sphere can be generated via the
\CRANpkg{geozoo} \citep{geozoo} package. We use PCA to estimate the 2D
space that is best suited to visualise the bases. The centre of the 2D
view is the first two PC coordinates of the zero matrix, and the radius
is estimated as the largest distance from the centre to the basis. The
theoretical best basis is known for simulated data and can be labelled
to compare how close the end basis found by the optimisers is to the
theoretical best. Various aesthetics, i.e.~size, alpha (transparency),
and colour, are applicable to emphasize critical elements and adjust for
the presentation. For example, anchor points and search points are less
important and hence a smaller size and alpha are used. Alpha can also be
applied on the interpolation paths to show the start to finish from
transparent to opaque.

@@

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/researh/paper-tour-vis/figs/toy-pca}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/researh/paper-tour-vis/figs/toy-pca-animated-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/researh/paper-tour-vis/figs/toy-tour-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/researh/paper-tour-vis/figs/toy-torus-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/researh/paper-tour-vis/figs/interruption-1}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/researh/paper-tour-vis/figs/polish-1}

@@

The holes index function used for all the examples before this section
produces a smooth interpolation, while this is not the case for all the
indexes. An example of a noisy index function for 1D projections
compares the projected data, \(\mathbf{Y}_{n \times 1}\), to a randomly
generated normal distribution, \(\mathcal{N}_{n \times 1}\), using the
Kolmogorov test. Let \(F_{.}(n)\) be the ECDF function (empirical
cummulative distribution function), with two possible subscripts \(Y\)
and \(\mathcal{N}\) representing the projected and randomly generated
data, and \(n\) denoting the number of observation, the Kolmogorov index
\(I^{nk}(n)\), is defined as:

@@

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/researh/paper-tour-vis/figs/noisy-better-geo}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/researh/paper-tour-vis/figs/kol-result}

@@

{\centering \includegraphics[width=1\linewidth]{/Users/sherryzhang/Documents/researh/paper-tour-vis/figs/flip-sign}
